### 2020-12-19 latex/introduction.tex
First edit of the intro, pre-lit review

\chapter{Introduction}
% TODO: Introduce the thesis with a short, sweet, intuitive approach.
% No math, just whet the reader's appetite for what we are doing. What are the motivating examples? Why do we study what we study? Why choose VNHCs over other methods?
Consider a child who is standing on a swing.
Naturally, the child pushes off the ground and starts bending and extending
their knees; they swing higher and faster over time, until they 
have reached their express goal of going as high and fast as possible.

Now imagine that the child is a robot, and their creator is teaching them to
swing like a real boy.
The first thing the roboticist might do is plot the leg motion of a human child
as a function of time and have the robot synchronize with this plot.
In an ideal world, this technique would work perfectly and the robot boy would
swing high, experiencing the same soaring feeling as his human counterpart.

Unfortunately, this behaviour is entirely unnatural. 
Humans on swings do not bend or extend their knees at specific times; rather,
they adjust their leg position based on the current angle of the swing along
with their direction of motion, as in Figure \ref{fig:swing-pos-vel}.
This position-velocity adjustment allows humans to correct for external
disturbances (like strong winds or overly enthusiastic parents).
Even if the robot could perfectly track a time-based trajectory, an external
disturbance may desynchronize the leg motion with the swing to the point that
the swing will slow down rather than speed up.

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{images/swing_pos_vel.png}
    \caption{A person on a standing swing will squat as they approach the
        bottom of the swing path, and stand after they pass it until they hit
        the peak of their swing. Image taken (with modifications) from
    \cite{pumping_swing_standing_squatting}.}
    \label{fig:swing-pos-vel}
\end{figure}

One recent control technique known as \textit{virtual holonomic constraints}
forces a robot's actuators to track a function of position rather than time.
Sadly, this still won't do for our robot boy because a real child also bends
their knees according to their direction of motion.
In other words, the robot's legs need to move as a function not only of
position, but also of velocity.

These are the types of controllers we study in this thesis: they are called
\textit{virtual nonholonomic constraints}.

>>>>

\chapter{Introduction}
% TODO: Introduce the thesis with a short, sweet, intuitive approach.
% No math, just whet the reader's appetite for what we are doing. What are the motivating examples? Why do we study what we study? Why choose VNHCs over other methods?
Consider a child on a standing swing.
Naturally, they push off the ground and proceed to alternate between standing
and squatting. 
This allows them to swing higher and faster over time, until they have reached
their express goal of going as high and fast as possible.

Now imagine that the child is a robot, and their creator is teaching them to
behave like a real boy.
If the roboticist had studied classical control theory, they would plot the leg
motion of a human child as a trajectory over time and tell the robot to
synchronize with this trajectory.
In an ideal world, this technique would work perfectly; unfortunately, this
control approach is entirely unnatural. 
Humans on swings do not have an internal stopwatch.
Rather, they adjust their leg position based on the current angle of the swing
along with their direction of motion, as in Figure \ref{fig:swing-pos-vel}.
This position-velocity adjustment allows humans to correct for external
disturbances (like strong winds or overly enthusiastic parents).
A person will squat at the peak of the swing and stand at the bottom.
Even if the robot could perfectly track a time-based trajectory, an external
disturbance may swap the order of squatting and standing to the point that
the swing slows down rather than speeding up.

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{images/swing_pos_vel.png}
    \caption{A person on a standing swing will squat as they approach the
        bottom of the swing path, and stand after they pass it until they hit
        the peak of their swing. Image taken and modified from
    \cite{pumping_swing_standing_squatting}.}
    \label{fig:swing-pos-vel}
\end{figure}

One recent control technique known as \textit{virtual holonomic constraints}
forces a robot's actuators to track a function of position rather than time.
Sadly, this will not work because one needs velocity to determine when
they have reached the peak of their swing.
In other words, the robot needs to move according to a function of both position
and velocity if it has any hope of behaving like a real person.

These position-velocity controllers are the focus of this thesis: they are called
\textit{virtual nonholonomic constraints}.
